### 2024-03-25 content/chapter_3.tex
:pencil: Add wave scattering models
:construction: Updating notations

\begin{section}{Introduction}
	\begin{subsection}{\glsfmtlong{swipt}}
		With the great advance in communication performance, a bottleneck of wireless networks has come to energy supply. \gls{swipt} is a promising solution to connect and power mobile devices via \gls{rf} waves. It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the \gls{iot} and \gls{m2m} networks. The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on \gls{wpt} and \gls{swipt} \cite{Clerckx2019}.

		The concept of \gls{swipt} was first cast in \cite{Varshney2008}, where the authors investigated the \gls{r-e} tradeoff for a flat Gaussian channel and typical discrete channels. \cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., \gls{ts} and \gls{ps}. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the \gls{r-e} region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the \gls{rf}-to-\gls{dc} conversion efficiency of rectifiers depends on the input power and waveform shape. It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for \gls{wpt}. Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}. A low-complexity adaptive waveform design by \gls{smf} was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}. Beyond \gls{wpt}, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to \gls{swipt} design, namely (i) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; (ii) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the \gls{r-e} region; (iii) a combination of \gls{ps} and \gls{ts} is generally the best strategy; (iv) the optimal input distribution is not the conventional \gls{cscg}; (v) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient \gls{swipt} design. Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for \gls{swipt} under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier \gls{swipt}, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier \gls{swipt}. The answers shed new light to the fundamental limits of \gls{swipt} and practical signaling (e.g., modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of \gls{cscg} and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger \gls{r-e} region compared to conventional \gls{cscg}. Recently, \cite{Varasteh2020a} used machine learning techniques to design \gls{swipt} signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
	\end{subsection}

@@

		Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation. \cite{Wu2018} proposed a \gls{ris}-assisted \gls{miso} system and jointly optimized the precoder at the \gls{ap} and the phase shifts at the \gls{ris} to minimize the transmit power. The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}. In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice. To estimate the cascaded \gls{ap}-\gls{ris}-\gls{ue} link without \gls{rf}-chains at the \gls{ris}, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}. The hardware architecture, design challenges, and application opportunities of practical \gls{ris} were covered in \cite{Wu2020}. In \cite{Dai2020}, a prototype \gls{ris} with \num{256} \num{2}-bit elements based on \gls{pin} diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
	\end{subsection}

	\begin{subsection}{\glsfmtshort{ris}-Aided \glsfmtshort{swipt}}
		By integrating \gls{ris} with \gls{swipt}, the constructive reflection can boost the end-to-end power efficiency and improve the \gls{r-e} tradeoff. In multi-user cases, dedicated energy beams were proved unnecessary for the weighted sum-power maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}. It was also claimed that \gls{los} links could boost the power efficiency since rank-deficient channels require fewer energy beams \cite{Wu2020a}. However, \cite{Wu2020b,Tang2019,Wu2020a} were based on a linear energy harvester model that is known in both the \gls{rf} and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}. Based on practical \gls{ris} and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based \gls{ris}-assisted \gls{swipt} system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage. The proposed framework provides a flexible tradeoff between performance and complexity. To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network. In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output \gls{dc} power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for \gls{swipt} with the passive beamforming capability of \gls{ris}, to investigate the \gls{r-e} tradeoff for one \gls{swipt} user with co-located information decoder and energy harvester. We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the \gls{r-e} region of \gls{ris}-aided \gls{swipt}?} The contributions of this paper are summarized as follows.

		\emph{First,} we propose a novel \gls{ris}-aided \gls{swipt} architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}. Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output \gls{dc} power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce \gls{dc}), waveform coupling (i.e., different waveforms jointly contribute to \gls{dc}), and high-order objective function. To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the \gls{ts} and \gls{ps} receiving modes. The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable \gls{r-e} region. This is the first paper to propose a joint waveform, active and passive beamforming architecture for \gls{ris}-aided \gls{swipt}.

		\emph{Second,} we characterize each \gls{r-e} boundary point by energy maximization under a rate constraint. The problem is solved by a \gls{bcd} algorithm based on the \gls{csit}. For active beamforming, we prove that the global optimal active information and power precoders coincide at \gls{mrt} even with rectifier nonlinearity. For passive beamforming, we propose a \gls{sca} algorithm and retrieve the \gls{ris} phase shift by eigen decomposition with optimality proof. Finally, the superposed waveform and the splitting ratio are optimized by the \gls{gp} technique. The \gls{ris} phase shift, active precoder, and waveform amplitude are updated iteratively until convergence. This is the first paper to jointly optimize waveform and active/passive beamforming in \gls{ris}-aided \gls{swipt}.

@@

		\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms. It is concluded that (i) \gls{ris} enables constructive reflection and flexible subchannel design in the frequency domain that is essential for \gls{swipt} systems; (ii) \gls{ris} mainly affects the effective channel instead of the waveform design; (iii) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; (iv) \gls{ts} is preferred at low \gls{snr} while \gls{ps} is preferred at high \gls{snr}; (v) there exist two optimal \gls{ris} development locations, one close to the \gls{ap} and one close to the \gls{ue}; (vi) the output \gls{snr} scales linearly with the number of transmit antennas and quadratically with the number of \gls{ris} elements; (vii) due to the rectifier nonlinearity, the output \gls{dc} scales quadratically with the number of transmit antennas and quartically with the number of \gls{ris} elements; (viii) for narrowband \gls{swipt}, the optimal active and passive beamforming for any \gls{r-e} point are also optimal for the whole \gls{r-e} region; (ix) for broadband \gls{swipt}, the optimal active and passive beamforming depend on specific \gls{r-e} point and require adaptive designs; (x) the proposed algorithms are robust to practical impairments such as inaccurate cascaded \gls{csit} and finite \gls{ris} reflection states.
	\end{subsection}
\end{section}

\begin{section}{System Model}\label{se:system_model}
	\begin{figure}[!t]
		\centering
		\def\svgwidth{0.9\columnwidth}
		\input{assets/chapter_3/system.eps_tex}
		\caption{An \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.}
		\label{fi:system}
	\end{figure}

@@

	\begin{subsection}{Transmitted Signal}
		Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency. The information signal transmitted over subband $n \in \{1, \dots, N\}$ at time $t$ is
		\begin{equation}
			\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
		\end{equation}
		where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$. On the other hand, the power signal transmitted over subband $n$ at time $t$ is
		\begin{equation}
			\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
		\end{equation}
		where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
		\begin{equation}
			\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
		\end{equation}
		We also define $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$.
	\end{subsection}

	\begin{subsection}{Reflection Pattern and Composite Channel}
		According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component. The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance. \gls{ris} element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
		\begin{equation}
			\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l},
		\end{equation}
		where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the \gls{ris}, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$. This paper sticks to the most common \gls{ris} model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical \gls{ris}-aided \gls{swipt}.} and $\theta_l \in [0,2\pi)$ is the phase shift. We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\boldsymbol{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the \gls{ris} vector and matrix, respectively.

		\begin{remark}\label{re:reflection_coefficient}
			The element impedance $Z_l$ maps to the reflection coefficient $\phi_l$ uniquely. Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands. In this paper, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each \gls{ris} element is the same at all subbands.
		\end{remark}

		At subband $n$, we denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the \gls{ap}-\gls{ris} incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the \gls{ris}-\gls{ue} reflected channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$. The auxiliary \gls{ap}-\gls{ris}-\gls{ue} link can be modeled as a concatenation of the incident channel, the \gls{ris} reflection, and the reflected channel. Hence, the composite equivalent channel reduces to
		\begin{equation}\label{eq:h_n}
			\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{h}_{\mathrm{R},n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\mathrm{I},n} = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n},
		\end{equation}
		where we define the cascaded incident-reflected channel at subband $n$ as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$. We also define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$.

		\begin{remark}\label{re:subband_tradeoff}
			The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies. Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier \gls{swipt}. For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$). That is to say, \gls{ris} essentially enables a flexible subchannel design. In the \gls{miso} case, a similar effect also exists in the spatial domain. Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
		\end{remark}
	\end{subsection}

	\begin{subsection}{Received Signal}
		The received superposed signal at the single-antenna \gls{ue} is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
		\begin{equation}
			y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})+\tilde{n}_n(t)\Bigr)}{e^{j2{\pi}{f_n}{t}}}\right\},
		\end{equation}
		where $\tilde{n}_n(t)$ is the noise at \gls{rf} band $n$. Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for information decoding.
	\end{subsection}

@@

			\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2

>>>>

\begin{section}{Introduction}
	\begin{subsection}{\glsfmtlong{swipt}}
		With the great advance in communication performance, a bottleneck of wireless networks has come to energy supply. \gls{swipt} is a promising solution to connect and power mobile devices via \gls{rf} waves. It provides low power at milliwatt level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the \gls{iot} and \gls{m2m} networks. The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on \gls{wpt} and \gls{swipt} \cite{Clerckx2019}.

		The concept of \gls{swipt} was first cast in \cite{Varshney2008}, where the authors investigated the \gls{r-e} tradeoff for a flat Gaussian channel and typical discrete channels. \cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., \gls{ts} and \gls{ps}. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the \gls{r-e} region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the \gls{rf}-to-\gls{dc} conversion efficiency of rectifiers depends on the input power and waveform shape. It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for \gls{wpt}. Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}. A low-complexity adaptive waveform design by \gls{smf} was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}. Beyond \gls{wpt}, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to \gls{swipt} design, namely:
		\begin{itemize}
			\item Modulated and unmodulated waveforms are not equally suitable for wireless power delivery;
			\item A multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the \gls{r-e} region;
			\item A combination of \gls{ps} and \gls{ts} is generally the best strategy;
			\item The optimal input distribution is not the conventional \gls{cscg};
			\item Modeling rectifier nonlinearity is beneficial to system performance and essential to efficient \gls{swipt} design.
		\end{itemize}
		Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for \gls{swipt} under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier \gls{swipt}, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier \gls{swipt}. The answers shed new light to the fundamental limits of \gls{swipt} and practical signaling (e.g., modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of \gls{cscg} and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger \gls{r-e} region compared to conventional \gls{cscg}. Recently, \cite{Varasteh2020a} used machine learning techniques to design \gls{swipt} signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
	\end{subsection}

@@

		Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation. \cite{Wu2018} proposed a \gls{ris}-assisted \gls{miso} system and jointly optimized the precoder at the \gls{ap} and the phase shifts at the \gls{ris} to minimize the transmit power. The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}. In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice. To estimate the cascaded \gls{ap}-\gls{ris}-\gls{ue} link without \gls{rf}-chains at the \gls{ris}, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}. The hardware architecture, design challenges, and application opportunities of practical \gls{ris} were covered in \cite{Wu2020}. In \cite{Dai2020}, a prototype \gls{ris} with \num{256} \num{2}-bit elements based on \gls{pin} diodes was developed to support real-time video transmission at gigahertz and mmWave frequency.
	\end{subsection}

	\begin{subsection}{\glsfmtshort{ris}-Aided \glsfmtshort{swipt}}
		By integrating \gls{ris} with \gls{swipt}, the constructive reflection can boost the end-to-end power efficiency and improve the \gls{r-e} tradeoff. In multi-user cases, dedicated energy beams were proved unnecessary for the weighted sum-power maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}. It was also claimed that \gls{los} links could boost the power efficiency since rank-deficient channels require fewer energy beams \cite{Wu2020a}. However, \cite{Wu2020b,Tang2019,Wu2020a} were based on a linear energy harvester model that is known in both the \gls{rf} and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}. Based on practical \gls{ris} and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based \gls{ris}-assisted \gls{swipt} system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage. The proposed framework provides a flexible tradeoff between performance and complexity. To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network. In this chapter, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output \gls{dc} power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for \gls{swipt} with the passive beamforming capability of \gls{ris}, to investigate the \gls{r-e} tradeoff for one \gls{swipt} user with co-located information decoder and energy harvester. We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the \gls{r-e} region of \gls{ris}-aided \gls{swipt}?} The contributions of this chapter are summarized as follows.

		\emph{First,} we propose a novel \gls{ris}-aided \gls{swipt} architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}. Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output \gls{dc} power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce \gls{dc}), waveform coupling (i.e., different waveforms jointly contribute to \gls{dc}), and high-order objective function. To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the \gls{ts} and \gls{ps} receiving modes. The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable \gls{r-e} region. This is the first work to propose a joint waveform, active and passive beamforming architecture for \gls{ris}-aided \gls{swipt}.

		\emph{Second,} we characterize each \gls{r-e} boundary point by energy maximization under a rate constraint. The problem is solved by a \gls{bcd} algorithm based on the \gls{csit}. For active beamforming, we prove that the global optimal active information and power precoders coincide at \gls{mrt} even with rectifier nonlinearity. For passive beamforming, we propose a \gls{sca} algorithm and retrieve the \gls{ris} phase shift by eigen decomposition with optimality proof. Finally, the superposed waveform and the splitting ratio are optimized by the \gls{gp} technique. The \gls{ris} phase shift, active precoder, and waveform amplitude are updated iteratively until convergence. This is the first work to jointly optimize waveform and active/passive beamforming in \gls{ris}-aided \gls{swipt}.

@@

		\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms. It is concluded that
		\begin{itemize}
			\item \gls{ris} enables constructive reflection and flexible subchannel design in the frequency domain that is essential for \gls{swipt} systems;
			\item \gls{ris} mainly affects the effective channel instead of the waveform design;
			\item Multisine waveform is beneficial to energy transfer especially when the number of subbands is large;
			\item \gls{ts} is preferred at low \gls{snr} while \gls{ps} is preferred at high \gls{snr};
			\item There exist two optimal \gls{ris} development locations, one close to the \gls{ap} and one close to the \gls{ue};
			\item The output \gls{snr} scales linearly with the number of transmit antennas and quadratically with the number of \gls{ris} elements;
			\item Due to the rectifier nonlinearity, the output \gls{dc} scales quadratically with the number of transmit antennas and quartically with the number of \gls{ris} elements;
			\item For narrowband \gls{swipt}, the optimal active and passive beamforming for any \gls{r-e} point are also optimal for the whole \gls{r-e} region;
			\item For broadband \gls{swipt}, the optimal active and passive beamforming depend on specific \gls{r-e} point and require adaptive designs;
			\item The proposed algorithms are robust to practical impairments such as inaccurate cascaded \gls{csit} and finite \gls{ris} reflection states.
		\end{itemize}
	\end{subsection}
\end{section}

\begin{section}{System Model}\label{se:system_model}
	\begin{figure}[H]
		\centering
		\def\svgwidth{0.9\columnwidth}
		\input{assets/chapter_3/system.eps_tex}
		\caption{An \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.}
		\label{fi:system}
	\end{figure}

@@

	\begin{subsection}{Transmitted Signal}
		Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency. The information signal transmitted over subband $n \in \{1, \dots, N\}$ at time $t$ is
		\begin{equation}
			\mathbf{x}_{\mathrm{I},n}(t) = \Re\left\{\mathbf{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
		\end{equation}
		where $\mathbf{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$. On the other hand, the power signal transmitted over subband $n$ at time $t$ is
		\begin{equation}
			\mathbf{x}_{\mathrm{P},n}(t) = \Re\left\{\mathbf{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
		\end{equation}
		where $\mathbf{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
		\begin{equation}
			\mathbf{x}(t) = \Re{\left\{\sum_{n=1}^N(\mathbf{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\mathbf{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
		\end{equation}
		We also define $\mathbf{w}_{\mathrm{I/P}} \triangleq [\mathbf{w}_{\mathrm{I/P},1}^\mathsf{T},\dots,\mathbf{w}_{\mathrm{I/P},N}^\mathsf{T}]^\mathsf{T} \in \mathbb{C}^{MN \times 1}$.
	\end{subsection}

	\begin{subsection}{Reflection Pattern and Composite Channel}
		According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component. The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance. \gls{ris} element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
		\begin{equation}
			\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l},
		\end{equation}
		where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the \gls{ris}, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$. This chapter sticks to the most common \gls{ris} model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical \gls{ris}-aided \gls{swipt}.} and $\theta_l \in [0,2\pi)$ is the phase shift. We also define $\mathbf{\phi} \triangleq [\phi_1, \dots, \phi_L]^\mathsf{H} \in \mathbb{C}^{L \times 1}$ and $\mathbf{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\mathbf{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the \gls{ris} vector and matrix, respectively.

		\begin{remark}\label{re:reflection_coefficient}
			The element impedance $Z_l$ maps to the reflection coefficient $\phi_l$ uniquely. Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands. In this chapter, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each \gls{ris} element is the same at all subbands.
		\end{remark}

		At subband $n$, we denote the \gls{ap}-\gls{ue} direct channel as $\mathbf{h}_{\mathrm{D},n}^\mathsf{H} \in \mathbb{C}^{1 \times M}$, the \gls{ap}-\gls{ris} incident channel as $\mathbf{H}_{\mathrm{F},n} \in \mathbb{C}^{L \times M}$, and the \gls{ris}-\gls{ue} reflected channel as $\mathbf{h}_{\mathrm{B},n}^\mathsf{H} \in \mathbb{C}^{1 \times L}$. The auxiliary \gls{ap}-\gls{ris}-\gls{ue} link can be modeled as a concatenation of the incident channel, the \gls{ris} reflection, and the reflected channel. Hence, the composite equivalent channel reduces to
		\begin{equation}\label{eq:h_n}
			\mathbf{h}_{n}^\mathsf{H} = \mathbf{h}_{\mathrm{D},n}^\mathsf{H} + \mathbf{h}_{\mathrm{B},n}^\mathsf{H} \mathbf{\Theta} \mathbf{H}_{\mathrm{F},n} = \mathbf{h}_{\mathrm{D},n}^\mathsf{H} + \mathbf{\phi}^\mathsf{H} \mathbf{V}_{n},
		\end{equation}
		where we define the cascaded incident-reflected channel at subband $n$ as $\mathbf{V}_{n} \triangleq \mathrm{diag}(\mathbf{h}_{\mathrm{B},n}^\mathsf{H})\mathbf{H}_{\mathrm{F},n} \in \mathbb{C}^{L \times M}$. We also define $\mathbf{h} \triangleq [\mathbf{h}_1^\mathsf{T},\dots,\mathbf{h}_N^\mathsf{T}]^\mathsf{T} \in \mathbb{C}^{MN \times 1}$.

		\begin{remark}\label{re:subband_tradeoff}
			The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies. Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier \gls{swipt}. For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\mathbf{\phi},n} \lVert \mathbf{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\mathbf{\phi}} \min_n \lVert \mathbf{h}_n \rVert$). That is to say, \gls{ris} essentially enables a flexible subchannel design. In the \gls{miso} case, a similar effect also exists in the spatial domain. Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
		\end{remark}
	\end{subsection}

	\begin{subsection}{Received Signal}
		The received superposed signal at the single-antenna \gls{ue} is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
		\begin{equation}
			y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\mathbf{h}_{n}^\mathsf{H}}{(\mathbf{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\mathbf{w}_{\mathrm{P},n})+\tilde{n}_n(t)\Bigr)}{e^{j2{\pi}{f_n}{t}}}\right\},
		\end{equation}
		where $\tilde{n}_n(t)$ is the noise at \gls{rf} band $n$. Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for information decoding.
	\end{subsection}

@@

			\lvert \mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n} \rvert^2
